Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-02-05 paper/ms.tex
Updated a couple of figures for Carlyn's paper.
figure touch-ups 1
Prettied up figures from Carlyn round 1.  A few more to do.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.png}
\caption{\label{fig:cumdist}
A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid models are shown in red, and the CO
models are shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens_v2.png}
\caption{\label{fig:masshighdens}
This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at the time of the DDT. 
The degree of expansion was found using the time at which the first detonation point occurred, and the mass at density less then 2e7 g/cc. The estimated Ni56 Yield is the final estimated mass of the model. 
Hybrid- Red
CO- Blue
For a given amount of mass at high density, the CO produces more Iron group elements then the Hybrid model.  
The rectangular regions show one stanadard deviation from the average for both the C/O and hybrid 
models (SEE DON'S PAPER)
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare.png}
\caption{\label{fig:compare}
The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio.png}
\caption{\label{fig:compare_ratio}
Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
SAME AS DON'S FIGURE 20.
}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
A plot of the estimated \Ni{56} yield as a function of the final, burned mass
for all CO and Hybrid runs. The Hybrid models are shown in red, and the CO
models are shown in blue. As it is shown, the CO model has a higher final mass
then the Hybrid model. 
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_vs_mass_at_high_dens.pdf}
\caption{\label{fig:masshighdens}
This is a plot of the estimated Ni56 yield vs. mass below 2e7 g/cc at the time of the DDT. 
The degree of expansion was found using the time at which the first detonation point occurred, and the mass at density less then 2e7 g/cc. The estimated Ni56 Yield is the final estimated mass of the model. 
Hybrid- Red
CO- Blue
For a given amount of mass at high density, the CO produces more Iron group elements then the Hybrid model.  
The rectangular regions show one stanadard deviation from the average for both the C/O and hybrid 
models (SEE DON'S PAPER)
}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:compare}
The conversion of Ni56 to Iron group elements are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons. 
First is that higher critical density leads to higher electron capture resulting in less Ni56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/compare_ratio_v2.png}
\caption{\label{fig:compare_ratio}
Figure 8 shows the evolution of the materials for both models. It is determined that the CO model had the greatest amount of Ni56, then the other IGE materials, compared to the hybrid model.  
SAME AS DON'S FIGURE 20.
}
\end{figure}
